Proportional multi-state multiple-cohort life table model

### 2018-04-03 MSLT/MSLTdoc.Rmd
Added bibliography file

---
title: "Proportional multi-state multiple-cohort life table model"
author: "Belen Zapata-Diomedi and Ali Abbas"
date: "26 March 2018"
header-includes:
    - \usepackage{setspace}\onehalfspacing

output:
  pdf_document: 
    toc: true
    number_sections: true
    fig_caption: yes
  fontsize: 12 pt
  geometry: margin=1in
  citation_package: natib
  bibliography: Bibliography.bib

---

@@

#Packages to run code
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
options(knitr.table.format = 'latex')
```
# Introduction

@@

The model was developed by Jan Barendregt and colleagues  and has been widely used in Australia and New Zealand ().

>>>>

---
title: "Proportional multi-state multiple-cohort life table model"
author: "Belen Zapata-Diomedi and Ali Abbas"
date: "26 March 2018"
header-includes:
    - \usepackage{setspace}\onehalfspacing
output:
   pdf_document: 
     toc: true
     number_sections: true
     fig_caption: yes
   fontsize: 12 pt
   geometry: margin=1in
bibliography: Bibliography.bib
---

@@

#Packages to run code
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
options(knitr.table.format = 'latex')
```
# Introduction

@@

The model was developed by Jan Barendregt and colleagues  and has been widely used in Australia and New Zealand [@RN38].
